The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables

### 2015-04-07 draft.tex
updated text

This revised model demonstrates that one can achieve a more
realistic optical spectrum by altering just two kinematic parameters. 
However, it may also be possible to achieve this with
other free parameters such as $\dot{M}_{wind}$, the opening angles of the wind and the 
inner and outer launch radii. For example, increasing the mass loss rate of the wind
would increase the amount of wind emission, as well as lowering the ionization 
parameter and increasing optical depth through the wind. In general, we expect
scattering and ionization changes to scale as $\rho$, whereas recombination
emission scales as $\rho^2$. Wider launch radii and opening angles would lead 
to a larger emitting volume, but this would be moderated by a decrease in density for a fixed mass-loss rate. 
We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
particularly affects the emergent spectrum seen at inclinations $<\theta_{min}$ as 
the inner disk is uncovered. A wind which extends right up to the WD would therefore
have more absorption in the resonance lines and a less pronounced Balmer absorption edge
at low inclinations. We suggest that future work should incorporate a treatment of clumping
and investigate the effect of these parameters in more detail. If a wind 
really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
understanding the true mass loss rate and geometry of the outflow is clearly important.

>>>>

This revised model demonstrates that one can achieve a more
realistic optical spectrum by altering just two kinematic parameters. 
However, it may also be possible to achieve this by modifying
other free parameters such as $\dot{M}_{wind}$, the opening angles of the wind and the 
inner and outer launch radii. For example, increasing the mass loss rate of the wind
increases the amount of recombination emission (which scales as $\rho^2$), 
as well as lowering the ionization parameter and increasing optical depth through the wind. 
Wider launch radii and opening angles lead to a larger emitting volume, but this is moderated by a decrease in density 
for a fixed mass-loss rate. We also note that the inner radius of $4~R_{WD}$ adopted by SV93 
affects the emergent UV spectrum seen at inclinations $<\theta_{min}$ as 
the inner disk is uncovered. This causes less absorption in the UV resonance lines,
but the effect on the optical spectrum is negligible.
We have verified this general behaviour, but
we suggest that future work should investigate the effect of these parameters in more detail
as well as incorporating a treatment of clumping.
If a wind really does produce the line and continuum emission seen in optical spectra of high-state CVs, then
understanding the true mass loss rate and geometry of the outflow is clearly important.
